R Notebook

### 2019-11-25 src/plots for paper.Rmd
plot updates

>>>>

#boxplots of env variables - part 2

```{r}
library(ggplot2)
library(gridExtra)
library(dplyr)

presab <- read.csv("../output/bio/presab_nafo_yr.csv", header = TRUE)
background <- subset(presab, occurrence == "0")

background <- filter(background, month !=1) #remove jan
background <- filter(background, month !=2) #remove feb

background$month <- factor(background$month) # converts month to a categorical variable

```{r}
box_temp <- ggplot(data = background, aes(x = month, y = temp_depth)) + geom_boxplot() + xlab("Month") + ylab("Temperature (Kelvin)") + theme_classic()

box_chl <- ggplot(data = background, aes(x = month, y = chl_surface)) + geom_boxplot() + xlab("Month") + ylab("Chlorophyll Concentration (mmol.m-3)") + theme_classic()

box_o2 <- ggplot(data = background, aes(x = month, y = o2_depth)) + geom_boxplot() + xlab("Month") + ylab("Dissolved Oxygen (mmol.m-3)") + theme_classic()

box_sal <- ggplot(data = background, aes(x = month, y = salinity_depth)) + geom_boxplot() + xlab("Month") + ylab("Salinity Concentration (PSU)") + theme_classic()

box_naos <- ggplot(data = background, aes(x = month, y = nao_sample)) + geom_boxplot() + xlab("Month") + ylab("NAO (Sampling Month)") + theme_classic()

box_amos <- ggplot(data = background, aes(x = month, y = amo_sample)) + geom_boxplot() + xlab("Month") + ylab("AMO (Sampling Month)") + theme_classic()

box_naop <- ggplot(data = background, aes(x = month, y = nao_prev)) + geom_boxplot() + xlab("Month") + ylab("NAO (Previous Month)") + theme_classic()

box_naow <- ggplot(data = background, aes(x = month, y = nao_winter)) + geom_boxplot() + xlab("Month") + ylab("NAO (Winter)") + theme_classic()

box_amow <- ggplot(data = background, aes(x = month, y = amo_winter)) + geom_boxplot() + xlab("Month") + ylab("AMO (Winter)") + theme_classic()

box_all <- grid.arrange(box_chl, box_o2, box_sal, box_temp, ncol=2)
ggsave("../output/maxent/paper_plots/env_boxplots.png", plot = box_all, device = png(), dpi = 400)

box_osc <- grid.arrange(box_naos, box_amos, box_naow, box_amow, box_naop, ncol = 3)
ggsave("../output/maxent/paper_plots/env_boxplots_osc.png", plot = box_osc, device = png(), dpi = 400)

box_aos <- grid.arrange(box_chl, box_o2, box_sal, box_temp,box_naos, box_amos, box_naow, box_amow, box_naop, ncol = 3)
ggsave("../output/maxent/paper_plots/env_boxplots_allos.png", plot = box_aos, device = png(), dpi = 400)

### 2019-11-25 src/testing_file.Rmd
plot updates

```{r bin probabilities}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
mthord <- c("jun") #"mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov",

@@

>>>>

```{r bin probabilities greater than}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
mthord <- c("jun") #"mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov",

@@

#calculate area encompassed by mcp

```{r}
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE) #existing file created
cumst1 <- cumst1[!cumst1$depth == "1387.38", ] #depth not needed
cumst1 <- cumst1[!cumst1$depth == "1265.86", ] #depth not needed
cumst1 <- cumst1[!cumst1$depth == "1151.99", ] #depth not needed

totalcell <- sum(cumst1$no_cells) #136467
totalcellkm <- totalcell*25 #3,461,675 km2 ?!
```

#boxplots of env variables - part 2

```{r}
library(ggplot2)
library(gridExtra)
presab <- read.csv("../output/bio/presab_nafo_yr.csv", header = TRUE)
background <- subset(presab, occurrence == "0")

background$month <- factor(background$month) # converts month to a categorical variable

```{r}
box_temp <- ggplot(data = background, aes(x = month, y = temp_depth)) + geom_boxplot() + xlab("Month") + ylab("Temperature (Kelvin)") + theme_classic()

box_chl <- ggplot(data = background, aes(x = month, y = chl_surface)) + geom_boxplot() + xlab("Month") + ylab("Chlorophyll Concentration (mmol.m-3)") + theme_classic()

box_o2 <- ggplot(data = background, aes(x = month, y = o2_depth)) + geom_boxplot() + xlab("Month") + ylab("Dissolved Oxygen (mmol.m-3)") + theme_classic()

box_sal <- ggplot(data = background, aes(x = month, y = salinity_depth)) + geom_boxplot() + xlab("Month") + ylab("Salinity Concentration (PSU)") + theme_classic()

box_naos <- ggplot(data = background, aes(x = month, y = nao_sample)) + geom_boxplot() + xlab("Month") + ylab("NAO (Sampling Month)") + theme_classic()

box_amos <- ggplot(data = background, aes(x = month, y = amo_sample)) + geom_boxplot() + xlab("Month") + ylab("AMO (Sampling Month)") + theme_classic()

box_naop <- ggplot(data = background, aes(x = month, y = nao_prev)) + geom_boxplot() + xlab("Month") + ylab("NAO (Previous Month)") + theme_classic()

box_naow <- ggplot(data = background, aes(x = month, y = nao_winter)) + geom_boxplot() + xlab("Month") + ylab("NAO (Winter)") + theme_classic()

box_amow <- ggplot(data = background, aes(x = month, y = amo_winter)) + geom_boxplot() + xlab("Month") + ylab("AMO (Winter)") + theme_classic()

box_all <- grid.arrange(box_chl, box_o2, box_sal, box_temp, ncol=2)
ggsave("../output/maxent/paper_plots/env_boxplots.png", plot = box_all, device = png(), dpi = 400)

box_osc <- grid.arrange(box_naos, box_amos, box_naow, box_amow, box_naop, ncol = 2)
ggsave("../output/maxent/paper_plots/env_boxplots_osc.png", plot = box_osc, device = png(), dpi = 400)

#make map with mcp eez and all landmass

```{r}
library(ggplot2)
library(raster)
library(rasterVis)

mcp <- shapefile("../output/bio/minimum_convex_poly/mcp_capelin_100_poly.shp")
aea <- raster("../output/env/aea.tif") #the correct projections
land <- shapefile("../data/env/landp/landpro.shp") #made in arcgis - aea proj
eez <- shapefile("../data/env/eez/maybethere.shp") # made in arc - aea proj

eezmap <- plot(mcp)
plot(eez, add = TRUE)
plot(land, add = TRUE)
```

#get median of env. data background points

```{r}
library(psych)

#presab <- read.csv("../output/bio/presab_nafo_yr.csv", header = TRUE)
#background <- subset(presab, occurrence == "0")

temp_depth <- describeBy(background$temp_depth, background$month, mat = TRUE, digits = 2)
temp_depth <- subset(temp_depth, select = c(group1, min, max, mean, median, range))
names(temp_depth)[names(temp_depth)=="group1"] <- "month"
write.csv(temp_depth, "../output/env/env_sumstats/temp_depth_background_summarystats_month.csv", row.names = FALSE)

salinity_depth <- describeBy(background$salinity_depth, background$month, mat = TRUE, digits = 2)
salinity_depth <- subset(salinity_depth, select = c(group1, min, max, mean, median, range))
names(salinity_depth)[names(salinity_depth)=="group1"] <- "month"
write.csv(salinity_depth, "../output/env/env_sumstats/salinity_depth_background_summarystats_month.csv", row.names = FALSE)

o2_depth <- describeBy(background$o2_depth, background$month, mat = TRUE, digits = 2)
o2_depth <- subset(o2_depth, select = c(group1, min, max, mean, median, range))
names(o2_depth)[names(o2_depth)=="group1"] <- "month"
write.csv(o2_depth, "../output/env/env_sumstats/o2_depth_background_summarystats_month.csv", row.names = FALSE)

chl_surface <- describeBy(background$chl_surface, background$month, mat = TRUE, digits = 2)
chl_surface <- subset(chl_surface, select = c(group1, min, max, mean, median, range))
names(chl_surface)[names(chl_surface)=="group1"] <- "month"
write.csv(chl_surface, "../output/env/env_sumstats/chl_surface_background_summarystats_month.csv", row.names = FALSE)

amo_sample <- describeBy(background$amo_sample, background$month, mat = TRUE, digits = 2)
amo_sample <- subset(amo_sample, select = c(group1, min, max, mean, median, range))
names(amo_sample)[names(amo_sample)=="group1"] <- "month"
write.csv(amo_sample, "../output/env/env_sumstats/amo_sample_background_summarystats_month.csv", row.names = FALSE)

amo_winter <- describeBy(background$amo_winter, background$month, mat = TRUE, digits = 2)
amo_winter <- subset(amo_winter, select = c(group1, min, max, mean, median, range))
names(amo_winter)[names(amo_winter)=="group1"] <- "month"
write.csv(amo_winter, "../output/env/env_sumstats/amo_winter_background_summarystats_month.csv", row.names = FALSE)

nao_sample <- describeBy(background$nao_sample, background$month, mat = TRUE, digits = 2)
nao_sample <- subset(nao_sample, select = c(group1, min, max, mean, median, range))
names(nao_sample)[names(nao_sample)=="group1"] <- "month"
write.csv(nao_sample, "../output/env/env_sumstats/nao_sample_background_summarystats_month.csv", row.names = FALSE)

nao_prev <- describeBy(background$nao_prev, background$month, mat = TRUE, digits = 2)
nao_prev <- subset(nao_prev, select = c(group1, min, max, mean, median, range))
names(nao_prev)[names(nao_prev)=="group1"] <- "month"
write.csv(nao_prev, "../output/env/env_sumstats/nao_prev_background_summarystats_month.csv", row.names = FALSE)

nao_winter <- describeBy(background$nao_winter, background$month, mat = TRUE, digits = 2)
nao_winter <- subset(nao_winter, select = c(group1, min, max, mean, median, range))
names(nao_winter)[names(nao_winter)=="group1"] <- "month"
write.csv(nao_winter, "../output/env/env_sumstats/nao_winter_background_summarystats_month.csv", row.names = FALSE)

```{r}
backaug <- subset(background, month == "8")
backj <- subset(background, month == "7")
backa <- subset(background, month = "4")
```
